\documentclass[titlepage, a4paper, 10pt]{report}
\usepackage[top=3.5cm, left=3cm, right=3cm, bottom=2.5cm]{geometry}
\usepackage[english]{babel}
\usepackage[unicode]{hyperref}
\usepackage{csquotes}
\usepackage{siunitx}
\usepackage{wrapfig}
\usepackage{footnote}
\usepackage[ruled,vlined,linesnumbered,longend]{algorithm2e}
\usepackage{titlesec}
\usepackage{titletoc}
\usepackage[font={small}]{caption}
\usepackage{subcaption}

% Citations and glossaries
\usepackage[toc,nonumberlist,nopostdot,acronyms,automake]{glossaries}
\usepackage[style=ieee]{biblatex}
\usepackage{bookmark}

% Color hyperlinks instead of having a box around them
\usepackage{listings}
\usepackage[table,xcdraw]{xcolor}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage[labelfont=bf]{caption}
\usepackage{float}

% Maths packages
\usepackage{amsmath, amssymb}
\usepackage{mathtools}
\usepackage{nicefrac}
\usepackage{multicol}

\usepackage{cleveref}

% Commands
\newcommand{\paper}[2]{#1 et al. \cite{#2}}
\newcommand{\thetitle}{Investigating non-invasive deep brain stimulation using temporally interfering electric fields}

% Colors
\definecolor{dark_grey}{HTML}{303030}

% PDF properties
\hypersetup{
  pdfauthor   = {Dimitrios Stoupis},
  pdftitle    = {\thetitle},
  pdfsubject  = {Bachelor thesis at the Department of Physics of the Aristotle University of Thessaloniki},
  pdfkeywords = {Neuroscience} {tTIS} {Thesis} {Brain} {Temporal Interference},
  colorlinks  = true, %Colours links instead of ugly boxes
  urlcolor    = blue, %Colour for external hyperlinks
  linkcolor   = dark_grey, %Colour of internal links
  citecolor   = blue %Colour of citations
}

\addbibresource{references.bib}

%\title{tACS using temporal interference to achieve targeted deep brain stimulation}
\title{\thetitle}
\author{Dimitrios Stoupis}
\date{}

\makeglossaries

% Highlight draft areas
\newcommand{\draft}[1]{{\leavevmode\color{red!90!black}#1}}

% Listing style
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}

\lstset{style=mystyle}
\pagenumbering{roman}

% Increase section depth
\setcounter{secnumdepth}{4}
\setcounter{tocdepth}{4}
\titleformat{\paragraph} [hang] {\normalfont\normalsize\bfseries} {\theparagraph} {1em} {}
%% End of package operations

%% Custom YAML highlight for the listing
% https://tex.stackexchange.com/questions/152829/how-can-i-highlight-yaml-code-in-a-pretty-way-with-listings
\newcommand\YAMLcolonstyle{\color{red}\ttfamily\footnotesize}
\newcommand\YAMLkeystyle{\color{black}\ttfamily\bf\footnotesize}
\newcommand\YAMLvaluestyle{\color{blue}\ttfamily\footnotesize}

\makeatletter

% here is a macro expanding to the name of the language
% (handy if you decide to change it further down the road)
\newcommand\language@yaml{yaml}

\expandafter\expandafter\expandafter\lstdefinelanguage
\expandafter{\language@yaml}
{
  keywords={true,false,null,y,n},
  keywordstyle=\color{darkgray}\bfseries,
  basicstyle=\YAMLkeystyle,                                 % assuming a key comes first
  sensitive=false,
  comment=[l]{\#},
  morecomment=[s]{/*}{*/},
  commentstyle=\color{purple}\ttfamily,
  stringstyle=\YAMLvaluestyle\ttfamily,
  moredelim=[l][\color{orange}]{\&},
  moredelim=[l][\color{magenta}]{*},
  moredelim=**[il][\YAMLcolonstyle{:}\YAMLvaluestyle]{:},   % switch to value style at :
  morestring=[b]',
  morestring=[b]",
  literate =    {---}{{\ProcessThreeDashes}}3
                {>}{{\textcolor{red}\textgreater}}1     
                {|}{{\textcolor{red}\textbar}}1 
                {\ -\ }{{\mdseries\ -\ }}3,
}

% switch to key style at EOL
\lst@AddToHook{EveryLine}{\ifx\lst@language\language@yaml\YAMLkeystyle\fi}
\makeatother

\newcommand\ProcessThreeDashes{\llap{\color{cyan}\mdseries-{-}-}}
%% End of custom YAML highlight for the listing

\begin{document}

\maketitle

\begin{abstract}
  Treating brain diseases or suppressing the symptoms is not a trivial task. Different methods exists and usually these are invasive, which inherently poses a great risk for the overall health of the individual. This one of the main reasons that there is a lot of research activity in the non-invasive methods and more specifically how to electromagnetically induce potentials or alter the behavior of neuronal networks. One drawback in most of the methods is the low temporal resolution accompanied by low penetration depth. Here a study on a set of human brain models\cite{ErikG.Lee2016} is presented, based on the \gls{tTIS} method, first introduced by Grossman et al.\cite{Grossman2017} and studied on a human brain model by Rampersad et al.\cite{Rampersad2019}. The scope of this report is to illustrate the potential problems or traits that will arise by simulating on a population human brain models. \draft{Info about the results required.}
\end{abstract}
\pagebreak


% \thispagestyle{empty}
% \setcounter{page}{0}
\tableofcontents
% \clearpage

% \pagebreak
% \cleardoublepage
% \phantomsection
% \addcontentsline{toc}{section}{\listfigurename}
\listoffigures
% \cleardoublepage
% \phantomsection
% \addcontentsline{toc}{section}{\listtablename}
\listoftables
% \cleardoublepage
% \phantomsection
% \addcontentsline{toc}{section}{\lstlistlistingname}
\lstlistoflistings

% Add the sections
\input{Sections/introduction.tex}
% \input{Sections/electrical_stimulation_methods.tex}
% \input{Sections/low_frequency_tacs_theory.tex}
\input{Sections/fe_modelling.tex}
\input{Sections/software_architecture.tex}
\input{Sections/simulation_results.tex}
\input{Sections/discussion_conclusion.tex}

% Helper sections
\input{glossary} % Input the glossary

% Print the glossary entries
\pagebreak
\printglossaries

% Print the references
\pagebreak
\printbibliography[heading=bibintoc]

\appendix
\input{Appendices/algorithms.tex}
\input{Appendices/snippets.tex}
\input{Appendices/code.tex}

\end{document}
